This is my paper title

### 2023-04-03 outputs/paper/paper.qmd
Correctly order of columns in graphs

clean_data_willingness |>
  ggplot(aes(x = grnprice)) +
  geom_bar(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Willingness to donate",
       y = "Number of respondents",
       title = "Willingness to donate to environmental protection")
```
\newpage
Talk way more about it.

@@

```
\newpage
Talk way more about it.

```{r}

@@

>>>>

clean_data_willingness |>
  ggplot(aes(x = grnprice)) +
  geom_bar(fill = "slateblue1") +
  theme_minimal() +
  labs(x = "Willingness to donate",
       y = "Number of respondents",
       title = "Willingness to donate to environmental protection")
```
@fig-2 talks about.

@@

```
@fig-4 talks about.

```{r}
#| label: fig-5
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

#clean_data |>
#  ggplot(mapping = aes(x = degrees_clean, fill = grnmoney)) +
# geom_bar(position = "dodge2")

@@

textbook 5.2.1
